Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations

### 2019-04-29 tex/main.tex
B&E reformating

\documentclass[journal=esthag,manuscript=article]{achemso}

@@

% authors
\author{Jonathan G. V. Ström}
\affiliation[Brown University]{Brown University, School of Engineering, Providence, RI, USA}
\author{Yuanming Guo}
\affiliation[Arizona State University]{Arizona State University, School of Sustainable Engineering and the Building Environment, Tempe, AZ, USA}
\author{Yijun Yao}
\affiliation[Brown University]{Brown University, School of Engineering, Providence, RI, USA}
\author{Eric M. Suuberg}
\email{eric_suuberg@brown.edu}
\affiliation[Brown University]{Brown University, School of Engineering, Providence, RI, USA}

% title
\title{Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations}

% keywords
\abbreviations{VI}
\keywords{Vapor intrusion, Preferential pathways, Temporal variability, Finite element modeling, Air exchange rate, Indoor/outdoor pressure difference}

@@

@@

\section{Introduction}

@@

\begin{figure}
 \caption{Typical data on indoor air TCE contaminant concentrations at the Indianapolis site\cite{u.s._environmental_protection_agency_assessment_2015}.}\label{fig:indianapolis}
 \includegraphics[width=\textwidth]{time_indianapolis.pdf}
\end{figure}

@@

\begin{figure}[htb!]
 \caption{Foundation and vadose zone soil represented in the modeling. Note that here a gravel sub-base material is shown, but in certain simulations, that material is absent and the surrounding soil directly contacts the foundation slab.  Different assumptions are made regarding the preferential pathway, here shown as a pipe entering the gravel sub-base. In some cases, the preferential pathway has been "turned off".}\label{fig:model}
 \includegraphics[width=\textwidth]{model.png}
\end{figure}

@@

@@

 \caption{Governing equations, boundary conditions \& model input parameters. (See below for table of nomenclature).}
 \label{tbl:eqns_bc_parameters}

@@

  \textbf{Boundary}            & \textbf{Richard's equation}              & \textbf{Advection-diffusion equation}                                      \\

@@

@@

\section{Results \& Discussion}

\subsection{Variation In Indoor Air Contaminant Concentration Over Time}

@@

\begin{figure}[htb!]
 \centering
 \caption{Mean values of the maximum change in indoor air contaminant concentration that may be expected
  over a given time period. (e.g., 1D is 1 day, 2W is 2 weeks, and 3M is 3 months). The error bars are the 95\% confidence intervals.}\label{fig:resampling}
 \includegraphics[width=\textwidth]{resampling.pdf}
\end{figure}

@@

\subsection{Statistical Analysis of Field Data}

@@

\begin{figure}[htb!]
 \centering
 \caption{2D-KDE plot showing the distributions of indoor air contaminant concentration, the indoor/outdoor pressure difference, and how they correlate to each other.}
 \label{fig:kde}
 \includegraphics[width=\textwidth]{nas_asu_pp.pdf}
\end{figure}

@@

\begin{table}[htb!]
 \caption{5th and 95th percentile values of $p_\mathrm{in/out}$ and $c_\mathrm{in}/c_\mathrm{in,mean}$ in Figure \ref{fig:kde}.}\label{tbl:percentiles}
 \begin{tabular}{c c c c c c c}
  \toprule
                                     & \multicolumn{2}{c|}{\textbf{North Island NAS}} & \multicolumn{2}{c|}{\textbf{ASU house PP Open}} & \multicolumn{2}{c}{\textbf{ASU House PP Closed}}                      \\
  Percentile                         & 5th                                            & 95th                                            & 5th                                              & 95th & 5th  & 95th \\
  $p_\mathrm{in/out}$ (Pa)           & -19.9                                          & 7.4                                             & -1.4                                             & 2.1  & -2.1 & 2.27 \\
  $c_\mathrm{in}/c_\mathrm{in,mean}$ & 4.1                                            & 0.2                                             & 13.5                                             & 0.2  & 3.3  & 0.4  \\
  \bottomrule
 \end{tabular}
\end{table}

\subsection{Variability Of Attenuation to Subslab Concentrations}

@@

\begin{figure}[htb!]
 \caption{Boxplot of $\log_{10}$ (subslab to indoor air contaminant attenuation) at the ASU house site. The box shows the quartiles of the distribution, the whiskers the extent of the distribution.}\label{fig:attenuation_subslab}
 \includegraphics[width=0.7\textwidth]{asu_attenuation_subslab.pdf}
\end{figure}

@@

\subsection{Modeling Results}

\subsubsection{Pressure Effects}

@@

\begin{figure}[htb!]
 \centering
 \caption{Simulated preferential pathway scenarios compared to actual ASU house field data. Field data are binned in 40 evenly spaced pressure bins, with the dot representing the mean and errors bars the 95\% confidence interval of data at a particular pressure range. Shaded blue represent the range of model predictions for the indicated pressure difference, due to air exchange rate variability (using 5th and 95th percentile values of measured exchange rates). Top panel is for various cases representing an "open" preferential pathway, the lower panel with the pathway "closed". }\label{fig:land_drain_scenarios}
 \includegraphics[width=\textwidth]{land_drain_scenarios_combo.pdf}
\end{figure}

@@

\subsubsection{Air Exchange Rate Effects}

@@

\begin{table}[htb!]
 \caption{Air exchange rate values (1/hr)}\label{tbl:air_exchange_rate}
 \begin{tabular}{l c c c}
  \toprule
  \textbf{Percentile}                                                     & \textbf{10th} & \textbf{50th} & \textbf{90th} \\
  EPA\cite{u.s._epa_exposure_2011,m._d._koontz_estimation_1995}           & 0.16-0.2      & 0.35-0.49     & 1.21-1.49     \\
  ASU house\cite{holton_temporal_2013,guo_identification_2015}            & 0.21          & 0.43          & 0.78          \\
  Indianapolis\cite{u.s._environmental_protection_agency_assessment_2015} & 0.34          & 0.74          & 1.27          \\
  \bottomrule
 \end{tabular}
\end{table}

@@

\subsubsection{Results of Transient Simulations}

@@

\begin{figure}
 \caption{Transient simulation of a "typical" VI day, using diurnal indoor/outdoor pressure difference and air exchange rate as inputs. Effect of preferential pathway considered.}\label{fig:diurnal}
 \includegraphics[width=\textwidth]{diurnal.pdf}
\end{figure}

@@

\begin{acknowledgement}
 This project was supported by grant ES-201502 from the Strategic Environmental Research and Development Program and Environmental Security Technology Certification Program (SERDP-ESTCP).
\end{acknowledgement}

\begin{table}[htb!]
  \caption{List of abbreviations}\label{tbl:abbreviations}
\begin{tabular}{l l}
  \toprule
  % A/ALPHA
  $A_\mathrm{ck}$ & Crack area \\
  $A_e$ & Air exchange rate \\
  $\alpha, \; n, \; m, \; l$ & van Genuchten parameters \\
  $\alpha_\mathrm{gw}$ & Attenuation from groundwater contaminant vapor source \\
  % C
  $c_\mathrm{in}$ & Indoor air contaminant concentration \\
  $c$ & Soil-gas contaminant concentration \\
  $c_w$ & Soil-water contaminant concentration \\
  $c_\mathrm{gw}$ & Contaminant groundwater concentration \\
  $\chi$ & Preferential pathway contaminant concentration scaling parameter \\
  % D
  $D_\mathrm{eff}$ & Effective diffusion coefficient \\
  $D_\mathrm{air}$ & Diffusion coefficient in air \\
  $D_\mathrm{water}$ & Diffusion coefficient in water \\
  % J
  $j_\mathrm{ck}$ & Contaminant molar flux through the foundation crack \\
  % K
  $\kappa_s$ & Saturated soil permeability \\
  $K_H$ & Dimensionless Henry's law constant \\
  $k_r$ & Relative permeability \\
  % L
  $L_\mathrm{slab}$ & Thickness of the foundation slab \\
  % M
  $M$ & Molar mass \\
  $\mu$ & Contaminant vapor viscosity \\
  % N
  NAS & Naval Air Stations \\
  % P
  $p$ & Pressure in soil \\
  $p_\mathrm{in/out}$ & Indoor/outdoor pressure difference \\
  PP & Preferential pathway \\
  % R
  $\rho$ & Density \\
  % S
  $\mathrm{Se}$ & Soil water saturation \\
  % T
  $t$ & time \\
  $\theta_g$ & Vapor/gas filled porosity \\
  $\theta_w$ & Water filled porosity \\
  $\theta_r$ & Residual water filled porosity \\
  $\theta_t$ & Total porosity \\
  % U
  $\vec{u}$ & Soil-gas velocity (vector quantity) \\
  % V
  VI & Vapor intrusion \\
  $V_\mathrm{base}$ & Basement volume \\
  % Z
  $z$ & Elevation above groundwater \\
  \bottomrule
\end{tabular}
\end{table}

\bibliography{library}

>>>>

\documentclass[preprint,12pt]{elsarticle}

@@

% keywords
%\abbreviations{VI}
%\keywords{}

\journal{Building \& Environment}

@@

\begin{frontmatter}
% title
\title{Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations}

% authors
\author[Brown]{Jonathan G. V. Ström}
\author[ASU]{Yuanming Guo}
\author[ASU]{Yijun Yao}
\author[Brown]{Eric M. Suuberg}

\ead{eric\_suuberg@brown.edu}

\address[Brown]{Brown University, School of Engineering, Providence, RI, USA}
\address[ASU]{Arizona State University, School of Sustainable Engineering and the Building Environment, Tempe, AZ, USA}

@@

\begin{keyword}
  Vapor intrusion \sep Preferential pathways \sep Temporal variability \sep Finite element modeling \sep Air exchange rate \sep Indoor/outdoor pressure difference
\end{keyword}

\end{frontmatter}

\section{Introduction}\label{s:intro}

@@

\begin{figure}
  \centering
 \includegraphics[width=\textwidth]{time_indianapolis.pdf}
 \caption{Typical data on indoor air TCE contaminant concentrations at the Indianapolis site\cite{u.s._environmental_protection_agency_assessment_2015}.}\label{fig:indianapolis}
\end{figure}

@@

\begin{figure}[htb!]
  \centering
 \includegraphics[width=\textwidth]{model.png}
 \caption{Foundation and vadose zone soil represented in the modeling. Note that here a gravel sub-base material is shown, but in certain simulations, that material is absent and the surrounding soil directly contacts the foundation slab.  Different assumptions are made regarding the preferential pathway, here shown as a pipe entering the gravel sub-base. In some cases, the preferential pathway has been "turned off".}\label{fig:model}
\end{figure}

@@

% TODO: Restructure entire table
\clearpage

@@

@@

  \textbf{Boundary}            & \textbf{Richard's equation}              & \textbf{Transport equation}                                      \\

@@

 \caption{Governing equations, boundary conditions \& model input parameters. (See below for table of nomenclature).}\label{tbl:eqns_bc_parameters}

@@

\section{Results \& Discussion}\label{s:results}

\subsection{Variation In Indoor Air Contaminant Concentration Over Time}\label{s:results_variation_time}

@@

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\textwidth]{resampling.pdf}
 \caption{Mean values of the maximum change in indoor air contaminant concentration that may be expected over a given time period. (e.g., 1D is 1 day, 2W is 2 weeks, and 3M is 3 months). The error bars are the 95\% confidence intervals.}\label{fig:resampling}
\end{figure}

@@

\subsection{Statistical Analysis of Field Data}\label{s:results_pressure_concentration}

@@

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\textwidth]{nas_asu_pp.pdf}
 \caption{2D-KDE plot showing the distributions of indoor air contaminant concentration, the indoor/outdoor pressure difference, and how they correlate to each other.}\label{fig:kde}
\end{figure}

@@

\begin{table}[htb!]
 \begin{tabular}{c c c c c c c}
  \toprule
                                     & \multicolumn{2}{c|}{\textbf{North Island}} & \multicolumn{2}{c|}{\textbf{ASU, PP Open}} & \multicolumn{2}{c}{\textbf{ASU, PP Closed}}                      \\
  Percentile                         & 5th                                            & 95th                                            & 5th                                              & 95th & 5th  & 95th \\
  $p_\mathrm{in/out}$ (Pa)           & -19.9                                          & 7.4                                             & -1.4                                             & 2.1  & -2.1 & 2.27 \\
  $c_\mathrm{in}/c_\mathrm{in,mean}$ & 4.1                                            & 0.2                                             & 13.5                                             & 0.2  & 3.3  & 0.4  \\
  \bottomrule
 \end{tabular}
 \caption{5th and 95th percentile values of $p_\mathrm{in/out}$ and $c_\mathrm{in}/c_\mathrm{in,mean}$ in Figure \ref{fig:kde}.}\label{tbl:percentiles}
\end{table}

\subsection{Variability Of Attenuation to Subslab Concentrations}\label{s:results_attenuation}

@@

\begin{figure}[htb!]
  \centering
 \includegraphics[width=0.7\textwidth]{asu_attenuation_subslab.pdf}
 \caption{Boxplot of $\log_{10}$ (subslab to indoor air contaminant attenuation) at the ASU house site. The box shows the quartiles of the distribution, the whiskers the extent of the distribution.}\label{fig:attenuation_subslab}
\end{figure}

@@

\subsection{Modeling Results}\label{s:results_modeling}

\subsubsection{Pressure Effects}\label{s:results_modeling_pressure}

@@

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\textwidth]{land_drain_scenarios_combo.pdf}
 \caption{Simulated preferential pathway scenarios compared to actual ASU house field data. Field data are binned in 40 evenly spaced pressure bins, with the dot representing the mean and errors bars the 95\% confidence interval of data at a particular pressure range. Shaded blue represent the range of model predictions for the indicated pressure difference, due to air exchange rate variability (using 5th and 95th percentile values of measured exchange rates). Top panel is for various cases representing an "open" preferential pathway, the lower panel with the pathway "closed".}\label{fig:land_drain_scenarios}
\end{figure}

@@

\subsubsection{Air Exchange Rate Effects}\label{s:results_modeling_air_exchange}

@@

\begin{table}[htb!]
 \begin{tabular}{l c c c}
  \toprule
  \textbf{Percentile}                                                     & \textbf{10th} & \textbf{50th} & \textbf{90th} \\
  EPA\cite{u.s._epa_exposure_2011,m._d._koontz_estimation_1995}           & 0.16-0.2      & 0.35-0.49     & 1.21-1.49     \\
  ASU house\cite{holton_temporal_2013,guo_identification_2015}            & 0.21          & 0.43          & 0.78          \\
  Indianapolis\cite{u.s._environmental_protection_agency_assessment_2015} & 0.34          & 0.74          & 1.27          \\
  \bottomrule
 \end{tabular}
 \caption{Air exchange rate values (1/hr)}\label{tbl:air_exchange_rate}
\end{table}

@@

\subsubsection{Results of Transient Simulations}\label{s:results_modeling_transient}

@@

\begin{figure}
  \centering
 \includegraphics[width=\textwidth]{diurnal.pdf}
 \caption{Transient simulation of a "typical" VI day, using diurnal indoor/outdoor pressure difference and air exchange rate as inputs. Effect of preferential pathway considered.}\label{fig:diurnal}
\end{figure}

@@

\section*{Acknowledgements}
This project was supported by grant ES-201502 from the Strategic Environmental Research and Development Program and Environmental Security Technology Certification Program (SERDP-ESTCP).

\appendix

\clearpage
\begin{table}[htb!]
  \caption{List of abbreviations}\label{tbl:abbreviations}
\begin{tabular}{l l}
  \toprule
  % A/ALPHA
  $A_\mathrm{ck}$ & Crack area \\
  $A_e$ & Air exchange rate \\
  $\alpha, \; n, \; m, \; l$ & van Genuchten parameters \\
  $\alpha_\mathrm{gw}$ & Attenuation from groundwater contaminant vapor source \\
  % C
  $c_\mathrm{in}$ & Indoor air contaminant concentration \\
  $c$ & Soil-gas contaminant concentration \\
  $c_w$ & Soil-water contaminant concentration \\
  $c_\mathrm{gw}$ & Contaminant groundwater concentration \\
  $\chi$ & PP contaminant concentration scaling parameter \\
  % D
  $D_\mathrm{eff}$ & Effective diffusion coefficient \\
  $D_\mathrm{air}$ & Diffusion coefficient in air \\
  $D_\mathrm{water}$ & Diffusion coefficient in water \\
  % J
  $j_\mathrm{ck}$ & Contaminant molar flux through the foundation crack \\
  % K
  $\kappa_s$ & Saturated soil permeability \\
  $K_H$ & Dimensionless Henry's law constant \\
  $k_r$ & Relative permeability \\
  % L
  $L_\mathrm{slab}$ & Thickness of the foundation slab \\
  % M
  $M$ & Molar mass \\
  $\mu$ & Contaminant vapor viscosity \\
  % N
  NAS & Naval Air Stations \\
  % P
  $p$ & Pressure in soil \\
  $p_\mathrm{in/out}$ & Indoor/outdoor pressure difference \\
  PP & Preferential pathway \\
  % R
  $\rho$ & Density \\
  % S
  $\mathrm{Se}$ & Soil water saturation \\
  % T
  $t$ & time \\
  $\theta_g$ & Vapor/gas filled porosity \\
  $\theta_w$ & Water filled porosity \\
  $\theta_r$ & Residual water filled porosity \\
  $\theta_t$ & Total porosity \\
  % U
  $\vec{u}$ & Soil-gas velocity (vector quantity) \\
  % V
  VI & Vapor intrusion \\
  $V_\mathrm{base}$ & Basement volume \\
  % Z
  $z$ & Elevation above groundwater \\
  \bottomrule
\end{tabular}
\end{table}

% TODO: Fix the natbib issues...
%\bibliographystyle{model1-num-names}
\bibliography{./library.bib}
